---
title: "P2_EthanSalcedo"
output: html_document
---

```{r}
#load packages
library(tidyverse) # includes ggplot2
library(magrittr) #allows for the assignment pipe %<>%
library(kableExtra) 
library(knitr) 
library(dplyr) 
library(DescTools) ## for phi and cramer's v functions
library(pwr) ## for power function
library(sjPlot) ## for tab_xtab
library(webshot) ## to convert html objects to images
```


Here we are loading the csv videogame sales data
```{r cars}
mydata <- read.csv("vgame_sales.csv")
glimpse(mydata)
```


Here we are doing the data cleaning.Remove any observations from the df that contain NA or a blank value for one or both of the variables (Genre & Rating).
```{r}

#One variable should be thought of as your x (independent) variable : Genre

#One variable should be thought of as your y (dependent) variable : Rating

#Both variables should be factors : COMPLETED

#Make sure you have observations in every cell : COMPLETED

#Review your two-way table if you have small cells turn them into bigger grou : COMPLETE
#All ratings that denote it is suitable for Everyone have been combined into a single level

mycopy <- mydata
#Rename the blank factor level in each variable in order to use the factor_recode function
levels(mycopy$Rating)[1] <- "DK/REF"
levels(mycopy$Genre)[1] <- "DK/REF"

#recode the factor levels "DK/REF" in each variable to NA values for removing and collapsing 
mycopy$Rating <- recode_factor(mycopy$Rating, "DK/REF"=NA_character_)
mycopy$Rating <- recode_factor(mycopy$Rating, "RP"=NA_character_)
mycopy$Genre <- recode_factor(mycopy$Genre, "DK/REF"=NA_character_, "Role-Playing"= "RPG", "Simulation"= "Sim")
mycopy$Genre <- fct_relevel(mycopy$Genre, sort)
#recode factor levels for Rating so that all kids aged ratings are together (separately from the DK/REF recode for clarity)
mycopy$Rating <- fct_collapse(mycopy$Rating,
                              E = c("E", "E10+", "EC", "K-A"),
                              M = c("M","AO"))
mycopy$Rating <- fct_relevel(mycopy$Rating, "E","T","M")


#remove the whole row if it is found to have a NA value for either Genre (x-value) or the Rating (y-value)
mycopy <- mycopy[!is.na(mycopy$Genre),]
mycopy <- mycopy[!is.na(mycopy$Rating),]

table(mycopy$Genre, mycopy$Rating)

#data is cleaned
```

Here we will write the code for the the Univariate Table
```{r}
#create two dataframes, each with 3 columns, Category, Frequency, and Percent.
#create a df for the genre and the rating variable
#creating the genre dataframe
genre_df <- mycopy %>%
  group_by(Genre) %>%
  summarize(Frequency = n(), Percent = paste(format(round(n()/nrow(mycopy)*100,1)), "%"))
names(genre_df)[1] <- "Category"
genre_df

#creating the Rating df
rate_df <- mycopy %>%
  group_by(Rating) %>%
  summarize(Frequency = n(), Percent = paste(format(round(n()/nrow(mycopy)*100,1)), "%"))
names(rate_df)[1] <- "Category"
rate_df

#combine the two dfs into one combined df using rbind(). the independent (Genre) variable should be stacked onto the depedent (Rating) variable

df_rage <- rbind(genre_df, rate_df)

tname <- "Figure 1 : Univariate Distribution of Genre and Rating"
titlehead <- c(tname=3)
names(titlehead) <- tname

unicat <- df_rage %>% kable(booktabs = T, align = "lcc") %>%
  kable_styling(full_width = FALSE) %>%
  pack_rows("Genre", 1, 12) %>%
  pack_rows("Rating", 13, 15) %>%
  add_header_above(header = titlehead, align = "l",
                   extra_css = "border-top: solid; border-bottom: double;") %>%
    row_spec(0, extra_css = "border-bottom: solid;") %>% 
    row_spec(nrow(df_rage), extra_css = "border-bottom: solid;") 
unicat
save_kable(unicat, "unicat_p2.png")
```

Code for creating the grouped bar chart
```{r}

genre_v_rating <- mycopy %>% group_by(Genre, Rating) %>% summarize(freq = n()) %>% ungroup() %>% group_by(Genre) %>% mutate(pct_within_genre = freq/sum(freq) *100)
genre_v_rating

#creating the bar chart
rating_ggplot <- genre_v_rating %>%
  ggplot(aes(fill = Rating, y = pct_within_genre, x = Genre)) +
  geom_bar(position="stack", stat="identity") +
  labs(x = "Genre",
       y = "Percent",
       title = "Figure 1 : Percent of Ratings by Genre") + 
       theme(legend.position = "bottom",
             legend.title = element_blank(),
             title = element_text(size=10),
             axis.title.x = element_text(size=10, color="black")) +
  geom_text(aes(label=ifelse(pct_within_genre >= 4.0,paste0(round(pct_within_genre, 0), "%"), "")),
            vjust=.5, color="white", size = 4, position=position_stack(vjust=0.5) 
           ) + 
  coord_flip() + 
  labs(y ="", x="") 
rating_ggplot
ggsave("p2bar.png", plot = rating_ggplot)
```

Here we will run the Chi-Square Test for Independence
```{r}
vg_rage <- mycopy
gen_tab <- table(mycopy$Genre, mycopy$Rating)
chisq.test(gen_tab)
```

Here we will be calculating the effect size (Cramer's V as the table is greater than 2x2)
```{r}
CramerV(gen_tab)
eff_size <- CramerV(gen_tab)

#the value is .462544 meaning that there is a large association between genre and rating
```

Two-Way table of variables in PQ format with Chi-Square results, effect size, and p-value
```{r}
rg_df <- mycopy[complete.cases(mycopy),]

two_tab <-tab_xtab(var.row = mycopy$Genre,
                   var.col = mycopy$Rating,
                   title = "Table 2: Chi-Square Test - Rating by Genre",
                   var.labels = c("Genre", "Rating"),
                   show.cell.prc = TRUE,
                   show.row.prc = TRUE,
                   show.summary = TRUE,
                   emph.total = TRUE,
                   emph.color = "#FFFFFF",
                   statistics = "cramer",
                   file = "boop.html")
two_tab
webshot("boop.html", "p2.png")
```

Power Analysis - Rejected Null | Determine the minimum sample size you could have to ensure power of 0.8
```{r}
pwr.chisq.test(w = eff_size, N = NULL, df = 22, sig.level = .5, power = .8)
```
The minimum sample size to achieve to ensure a power of 0.8 is 31.

Exporting data to .RDS file
```{r}
saveRDS(mycopy, file = "cleaned_p2.rds")
```

