---
title: "Project 1 : Descriptive Statistics and Visualization"
output: html_notebook
author: Ethan Salcedo
---

```{r}
#load packages
library(tidyverse) #includes ggplot2
library(descr) #used for two-way CrossTable()
library(ggpubr) #contains line/dot plot for visualizing means 
library(magrittr) # so you can use the assignment pipe %<>%
library(dplyr) 
library(flextable) ## generates PQ freq/summary tables in .doc or .pdf
library(webshot) #required to save flextables and ggplot2 objects as imgs
library(sjPlot) #PQ two-way/contingency table
library(stargazer) # PQ numerical summary stats
library(ggthemes) # imports preset themes for use with ggplot2
```

Loading CSV file into RStudio
```{r}
mydata <- read.csv(file="/Users/salcetoes/Desktop/RStudio/videogame-analysis-main/vgame_sales.csv", header=TRUE, na.strings = (""))
glimpse(mydata)
```

Look at descriptive statistics for your variables (PQ table or chart)
Here you will clean the variables and prepare the data

We will be using the following variables : Critic_Score, User_Score, NA/JP/EU Sales, Global Sales, Genre, Release Year, Rating 

```{r}
descr_data <- as.data.frame(mydata)

# mutate before factoring
descr_data <- descr_data %>%
  mutate(User_Score = replace(User_Score, User_Score == 'tbd', NA),
         Year_of_Release = replace(Year_of_Release, Year_of_Release == "N/A", NA))

# convert metrics into numeric format
descr_data$User_Score <- as.numeric(descr_data$User_Score)
descr_data$User_Count <-as.numeric(descr_data$User_Count)
descr_data$Critic_Count <- as.numeric(descr_data$Critic_Count)
descr_data$Critic_Score <- as.numeric(descr_data$Critic_Score)

# automated character columns -> factor columns
# subsets the columns in descr_data that is.character returns TRUE
# lapply() applies the as.factor function to the subset of descr_data with only chr columns
descr_data[sapply(descr_data, is.character)] <- lapply(descr_data[sapply(descr_data, is.character)], as.factor)

glimpse(descr_data)

# cleaned Genre, Critic_Score, User_Score, and Rating
descr_data <- descr_data %>% drop_na(Critic_Score, User_Score, Critic_Count, User_Count)
descr_data$Year_of_Release <- droplevels(descr_data$Year_of_Release)
descr_data$Platform <- droplevels(descr_data$Platform)
table(descr_data$Platform)
```

Create a table that shows Genres on the vertical axis and average metacritic and average user scores on the horizontal 
```{r}

genre_table <-
  descr_data %>% mutate(Genre = fct_infreq(Genre)) %>%
  group_by(Genre) %>%
  summarize('Number of Games' = n(),
            'Average Meta Score' = format(round(mean(Critic_Score),2)),
            'Average User Score' = format(round(mean(as.numeric(User_Score)),2))
            )

flex_genre <- flextable(genre_table)

flex_genre2 <- add_header_lines(flex_genre, 'Table 1 : Average Metacritic/User Scores and Metacritic/User Count Based on Genre')
flex_genre3 <- align(flex_genre2, align = 'center', part = 'all', j = 2:4)

autofit(flex_genre3)

## save_as_image(flex_genre4, path = "genre_table.png")

```
```{r}
genre_sales <- 
  descr_data %>% mutate(Genre = fct_infreq(Genre)) %>%
  group_by(Genre) %>%
  summarize(
            "Global" = format(round(mean(Global_Sales*10),2)),
            "North America" = format(round(mean(NA_Sales*10),2)),
            "Japan" = format(round(mean(JP_Sales*10),2)),
            "Europe" = format(round(mean(EU_Sales*10),2)),
            "Other" = format(round(mean(Other_Sales*10),2)))
genre_sales <- flextable(genre_sales)
genre_sales2 <- autofit(genre_sales)
genre_sales3 <- add_header_lines(genre_sales2, "Table 2 : Average Sales (in hundred thousands) of Games by Genre and Region")
genre_sales3

save_as_image(genre_sales3, path = "region_table1.png")
```

Rating and Global Sales

```{r}
mycopy <- descr_data

# combine similar ratings into single category
mycopy$Rating <- fct_recode(mycopy$Rating, E = 'E10+', E = 'EC', E = 'K-A', E ='E',  NRA = "RP", M ="AO")

levels(mycopy$Rating)
levels(mycopy$Rating) <- c("Mature", "Everyone", "NRA", "Teen")

rating_graph <- mycopy %>% filter(Rating == 'Mature' | Rating == 'Everyone' | Rating == 'Teen') %>%
  mutate(Rating = fct_infreq(Rating)) %>%
  ggplot(aes(y = NA_Sales, x = Rating, fill = Rating)) +
    geom_boxplot(outlier.size = 0, outlier.shape = NA) +
    coord_flip(ylim = c(0,1))+
    theme(legend.position = "none", panel.grid.major.y = element_blank()) +
    labs(x = "ESRB Rating", y = "NA Sales (in millions of units)", title = "Figure 1 : Rating vs North American Sales")

rating_graph
ggsave("ratinggraph.png")
```

-
This portion of code create the 'Metacritic Score vs. Global Sales' scatterplot graph 

```{r}
sales <- descr_data
bold.11.text <- element_text(face='bold', size = 11)
global_graph <- ggplot(sales, aes(x = Critic_Score, y = Global_Sales)) + 
  geom_point(color = 'darkgreen') +  
  
  ylim(0, 40) +
  geom_smooth(method = loess, se = FALSE)

global_graph +
  labs( x = "Metacritic Score", y = "Global Sales (in millions of units)",
    title = "Figure 2 : Metacritic Score vs Global Sales") 

ggsave("metaglobal.png")

```

